### 2023-03-12 main/chapter_2ljets.tex
add some future lhc content

No end is in sight for SUSY searches, but future LHC collision data will
continue to push the high-mass frontier of sensitivity for the supersymmetric
models considered in this thesis.
% - second wave not happening
\atlas\ has published `second-wave' Run~2 papers for some similar searches,
which re-analyse the Run~2 data with refined techniques or more focussed
objectives~\cite{
ATLAS:2022hbt,
ATLAS:2022nrb
},
but the recent date of $\twoljets$'s publication suggests that \atlas\ will
use Run~3 data in its next paper on the topic.
% - Run 3 expected luminosity
% - HL-LHC
TODO~\cite{ZurbanoFernandez:2020cco}
% - If a future collider is constructed, then...

>>>>

No end is in sight for SUSY searches, but future LHC collision data will
continue to push the high-mass frontier of sensitivity for the supersymmetric
models considered in this thesis.
% - second wave not happening
\atlas\ has published `second-wave' Run~2 papers for some similar searches,
which re-analyse the Run~2 data with refined techniques or more focussed
objectives~\cite{
ATLAS:2022hbt,
ATLAS:2022nrb
},
but the recent date of $\twoljets$'s publication suggests that \atlas\ will
use Run~3 data in its next paper on our topic.
% - Run 3 expected luminosity
In Run~3, the LHC is only operating at a marginally increased centre-of-mass energy
of $\sqrt{s} = 13.6\,\eV[T]$~\cite{run3sqrts};
its main benefit will therefore be the increased data quantity,
for which a a recent projection indicates a target integrated luminosity of
$250\,\mathrm{fb}^{-1}$ for $pp$ collisions by the year
2025~\cite{run3luminosity},
on top of the $139\,\mathrm{fb}^{-1}$ of Run~2.
Given similar collision conditions, this will allow sensitivity to rare signals
with proportionately small cross-sections.

% - HL-LHC
TODO
- around $300\,\mathrm{fb}^{-1}$ to $400\,\mathrm{fb}^{-1}$ per year
- pile-up of around $200$ interactions per bunch crossing
- relative to around $50$ interactions per bunch crossing in Run~2~\cite{ATLAS:2022hro}
TODO~\cite{ZurbanoFernandez:2020cco}
% - If a future collider is constructed, then...
